%----------------------------------------------------------------------------------------
%	SECTION A
%----------------------------------------------------------------------------------------

\newpage

\thispagestyle{empty}

\chaptertitle{Session-1}{How to talk about personality types-1}

\newpage

\chapterheader{Session-1}{How to talk about personality types-1}


\entry{Egotism}{ego-tism}{Noun}{The belief that you are better or important than other people.}

\entry{Conceit}{}{}{Too much pride in your own worth or goodness.}

\entry{Amorous}{}{}{Having feeling of sexual attraction or love.}

\entry{Boast}{}{}{Too much pride in yourself.}

\entry{Obnoxious}{}{}{Unpleasant in a way that makes people feel offended.}

\entry{Monotonous}{}{}{Something that is boring because it is the same.}

\entry{Egotist}{}{}{One who have too much pride in it own wroth or goodness.}

\entry{Altrusim}{}{}{Desire to help other people.}

\entry{Futile}{}{}{Pointless or useless.}

\entry{Nag}{}{}{Annoy}

\entry{Solitude}{}{}{Situation in which you are alone usally because you want to be.}

\entry{Introvert}{}{}{A shy person.}

\entry{Extrovert}{}{}{A friendly person who likes being with and talking to other people.}

\entry{Ambivert}{}{}{A person having characteristics of both extrovert and introvert.}

\entry{Cynical}{}{}{Selfish and dishonest.}

\entry{Embitter}{}{}{To cause bitter feeling in (someone).}

\entry{Misanthrope}{}{}{A person who does not like other people.}

\entry{Scorn}{}{}{Lack of respect for someone.}

\entry{Misogynist}{}{}{One who hate woman.}

\entry{Misogamist}{}{}{One who hate marriage.}

\entry{Self-denial}{}{}{The act of not allowing yourself to have or to do something you want.}

\entry{Autertity}{}{}{Simple and plain quality. A situation in which there is not much money and it is spent only on things that are necessary.}

\entry{Contemplation}{}{}{Thinking deeply about something.}

\entry{Ascetic}{}{}{Simple way of living that avoids physical pleasure.}








